Towards Language Model-based Identification of Business Clusters

### 2023-07-02 paper/paper.tex
adjustments to paper & report

\include{./wits_template.zex}

@@

\author{Nicola J. Müller, Robert Leist, Paul Eichler, \\and Tobias Recktenwald}
\title{Towards Language Model-based Identification of Market Segments and Fostering of Business Clusters}

\begin{document}
    \maketitle
   \begin{abstract}
   	Identifying market segments is crucial for effective marketing strategies and well-informed business decisions. Further, combining companies' geographical locations with their market segments allows for detecting business clusters. However, acquiring and processing the data needed to gain such insights into regional economies is labor-intensive.

   	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform companies' highly informative public text data into low-dimensional vectors and then applying clustering to identify market segments and make location recommendations for novel companies to support business cluster development.

   	A qualitative evaluation of our methods being applied to data from the German municipality Saarland demonstrates that our methods can accurately cluster similar companies and assign novel companies to existing clusters.
   \end{abstract}

@@

   Business clusters are local concentrations of companies, manufacturers, suppliers, and institutions from the same field. Identifying clusters combines geographical data of companies' locations with information on their corresponding market segments. This proximity of related companies enables efficient cooperation and knowledge transfer, which has been shown to significantly increase the productivity of all companies within the cluster \cite{clustersandcomp,gems-model, regionaladv, clustertheory}. Thus, establishing or further developing business clusters is of high interest to companies and local governments. Therefore, significant effort is spent identifying clusters and market segments in regional economies.

   However, identifying market segments and business clusters requires a significant amount of manual labor. Typically, one must first collect information about companies in the targeted region. Afterward, for each company, their publicly available information must be analyzed to understand their products, strategic position, market positioning, and further characteristics. 
   This process is labor-intensive, as businesses do not provide specific data on the latter points, but it must be inferred from their product portfolio and websites. Additionally, even basic data like the number of employees is often unavailable or difficult to collect automatically, especially for small regional companies.
   At the same time, recent advances in natural language processing (NLP), e.g., the popular ChatGPT \cite{chatgpt}, have yielded surprisingly good results in numerous applications. Especially they have proven to be very efficient at extracting data and summaries from human written texts.

@@

   Business clusters and their advantages have been studied in many works. For example, \cite{regionaladv} examined the well-known technology cluster in Silicon Valley, famous for being the home of many innovative start-ups. 
   \cite{clustertheory} provides a detailed discussion of the cluster phenomenon. It discusses preexisting literature on clusters and reviews the main positive effects commonly observed in clusters, positive feedback and productivity \& growth. Additionally, it provides examples of well-known clusters.

   The region of choice for testing our approach, Saarland, has also been the subject of scientific work. It should be noted that Saarland is mostly investigated for its location on the border of France and Luxembourg or because of its mining and steel-producing past.
   These factors are, however, of no interest to this work. For example, \cite{saarlandeco1} has focused on the agglomeration of the automotive industry in Saarland and the neighboring regions but focuses on the challenges that the country borders pose to this industry.
   The paper \cite{saarlandeco2} specifically compares the economic strategies for developing the region's economy with a focus on how clusters are developed. Most importantly, they identify some regional business clusters. We will revisit these when evaluating our clustering algorithm and compare the clusters and market segments identified by our approach. It should be noted, however, that the paper was published in 2009, meaning their analysis could be outdated to some extent.

@@

   A qualitative evaluation of our methods has shown that they can reliably cluster similar companies, which allowed us to infer market segments in Saarland. Further, our location recommendation system demonstrated its capability of identifying similar companies, given the description of a new company.

   To allow end-users to leverage our methods, we implemented a user-friendly interface with many functionalities, such as visualizing the clustered data points, showing the location of companies, and giving detailed and interpretable location recommendations.

@@

   To this end, we have demonstrated the feasibility and potential of applying language models to economic analysis.

>>>>

\include{./wits_template.tex}

@@

\author{\small \href{mailto:s8namuel@stud.uni-saarland.de}{Nicola J. Müller}, \href{s8roleis@stud.uni-saarland.de}{Robert Leist}, \href{mailto:s8pleich@uni-saarland.de}{Paul Eichler}, and \href{mailto:s8tsreck@stud.uni-saarland.de}{Tobias Recktenwald}}
\title{\vspace{-3cm}Towards Language Model-based Identification of Business Clusters}
\date{}

\begin{document}

    \maketitle

   \begin{abstract}

	\textit{\small
	One of the most important decisions every business has to decide on a physical location. Identifying the right location is crucial for effective marketing strategies reaching the intended customer base, it can reduce transportation costs, and locating in a vibrant regional business clusters can have significant positive effects on business development.
	However, strategically acquiring \& analyzing data on regional economies, the corresponding companies along with their target market segments is very complex and labor-intensive.}
	\textit{\small
	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform publicly available company websites, into machine-readable data points and  applying clustering to make location recommendations. We demonstrate accuracy of identified clusters by applying our method to data from the German municipality Saarland.
	}
   \end{abstract}

@@

   Business clusters are local concentrations of companies, manufacturers, suppliers, and institutions from the same field. Identifying clusters combines geographical data of companies' locations with information on their corresponding market segments. This proximity of related companies enables efficient cooperation and knowledge transfer, which has been shown to significantly increase the productivity of all companies within the cluster \cite{clustersandcomp,gems-model, regionaladv, clustertheory}. Thus, establishing or further developing business clusters is of high interest to companies and local governments. Therefore, significant effort is spent identifying clusters in regional economies.

   However, them requires a significant amount of manual labor. Typically, one must first collect information about companies in the targeted region. Afterward, for each company, their publicly available information must be analyzed to understand their products, strategic position, market positioning, and further characteristics. 
   This process is labor-intensive, as businesses do not provide specific data on the latter points, but it must be inferred from their product portfolio and websites. Additionally, even basic data like the number of employees is often unavailable or difficult to collect automatically, especially for small regional companies.
   At the same time, recent advances in natural language processing (NLP), e.g., the popular ChatGPT \cite{chatgpt}, have yielded surprisingly good results in numerous applications. Especially they have proven to be very efficient at extracting data and summaries from human written texts.

@@

   Business clusters and their advantages have been studied in many works. For example, \cite{regionaladv} examined the well-known technology cluster in Silicon Valley, famous for being the home of many innovative start-ups. 
   \cite{clustertheory} provides a detailed discussion of the cluster phenomenon. It discusses preexisting literature on clusters and reviews the main positive effects commonly observed in clusters, positive feedback and productivity \& growth. Additionally, it provides examples of well-known clusters.
   The region of choice for testing our approach, Saarland, has also been the subject of scientific work. It should be noted that Saarland is mostly investigated for its location on the border of France and Luxembourg or because of its mining and steel-producing past.
   These factors are, however, of no interest to this work. For example, \cite{saarlandeco1} has focused on the agglomeration of the automotive industry in Saarland and the neighboring regions but focuses on the challenges that the country borders pose to this industry.
   The paper \cite{saarlandeco2} specifically compares the economic strategies for developing the region's economy with a focus on how clusters are developed. Most importantly, they identify some regional business clusters. We will revisit these when evaluating our clustering algorithm and compare the clusters and market segments identified by our approach. It should be noted, however, that the paper was published in 2009, meaning their analysis is outdated to some extent.

@@

   A qualitative evaluation of our methods has shown that they can reliably cluster similar companies, which allowed us to infer market segments in Saarland. Further, our location recommendation system demonstrated its capability of identifying similar companies, given the description of a new company. To allow end-users to leverage our methods, we implemented a user-friendly interface with many functionalities, such as visualizing the clustered data points, showing the location of companies, and giving detailed and interpretable location recommendations.

@@

### 2023-07-02 report/report.tex
adjustments to paper & report

\title{Towards Language Model-based Identification of Market Segments and Fostering of Business Clusters}

@@

\begin{abstract}
	Identifying market segments is crucial for effective marketing strategies and well-informed business decisions. Further, combining companies' geographical locations with their market segments allows for detecting business clusters. However, acquiring and processing the data needed to gain such insights into regional economies is labor-intensive.

	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform companies' highly informative public text data into machine-readable data points and then applying clustering to identify market segments and make location recommendations for novel companies to support business cluster development.

	A qualitative evaluation of our methods being applied to data from the German municipality Saarland demonstrates that our methods can accurately cluster similar companies and assign novel companies to clusters.
\end{abstract}

>>>>

\title{Towards Language Model-based Identification of Business Clusters}

@@

\begin{abstract}
	One of the most important decisions every business has to decide on a physical location. Identifying the right location is crucial for effective marketing strategies reaching the intended customer base, it can reduce transportation costs, and locating in a vibrant regional business clusters can have significant positive effects on business development.
	However, strategically acquiring \& analyzing data on regional economies, the corresponding companies along with their target market segments is very complex and labor-intensive.

	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform publicly available company websites, into machine-readable data points and  applying clustering to make location recommendations for novel.

	A qualitative evaluation of our methods being applied to data from the German municipality Saarland demonstrates that our methods can accurately cluster related companies and categorize novel companies to a cluster.
\end{abstract}
